Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-27 Latex/tex/pr.tex
change latex2

In this paper, as  depicted in figure \ref{fig:c11}, the downlink of the O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide requirements of services. Optimal power allocation and joint mapping slices to services are applied. In addition, mapping slices to physical resources is taken to account.\newline
In \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed. Also, problem statements is explained and decomposed to two
different sub-problems. 
In \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In \ref{simul}, numerical results, is depicted for the sub-problems.

@@

Each packet is processed by one of the VNFs of slices. So the mean delay of the $s^{th}$ slice in the first layer which is modeled as M/M/1 queue from queuing theory is formulated as

@@

d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}.

@@

Also, the delay of $s^{th}$ slice in the second layer is
d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.

>>>>

In this paper, as  depicted in figure \ref{fig:c11}, the downlink of the O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide requirements of services. Optimal power allocation and joint mapping slices to services are applied. In addition, mapping slices to physical resources is taken to account.\newline
The contribution of the paper is expressed as follow:
\begin{itemize}
\item In this paper, joint RAN slicing and resource allocation is considered in an end to end O-RAN system.
\item UEs are categorized into different class of services based on their service requirements. RAN which contains RRHs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.  
\item The problem is decomposed into two independent sub-problems. 
\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
\end{itemize}

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed. Also, problem statements is explained and decomposed to two
different sub-problems. 
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results, is depicted for the sub-problems.

@@

Each packet is processed by one of the VNFs of slices. So the mean delay of the $s^{th}$ slice in the first and the second layer, which is modeled as M/M/1 queue from queuing theory, is formulated as follow
,respectively

@@

d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}} \\
d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.

@@

where, $\mu_1$ and $\mu_2$ is the computational capacity of the first and the second layer respectively.
